---
title: "PW7"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r pressure, echo=FALSE}
library(FactoMineR)
library(factoextra)
```
```{r}
data(decathlon2)
head(decathlon2)
```

#3
```{r}
str(decathlon2)
```

#4

```{r}
decathlon2.active<-decathlon2[1:23,1:10]

```

```{r}
res.pca<-PCA(decathlon2.active,graph=FALSE)

```

#q6
```{r}
print(res.pca)
```
#q7
```{r}
eig.val<-get_eigenvalue(res.pca)
eig.val

#Ici le tableau de retour la col2[i]=nblignes*col1[i]
```

#q8
```{r}
fviz_eig(res.pca,addlabels=TRUE,ylim=c(0,50))


```

#q9

```{r}
fviz_pca_var(res.pca,col.var="black")
```

#q10
```{r}
head(res.pca$var$cos2,4)
```


#q11
```{r}
fviz_pca_var(res.pca,col.var="cos2",gradient.cols=c("#00AFBB","#E7B800","#FC4E07"),repel=TRUE)

```
#q12
```{r}
res.desc<-dimdesc(res.pca,axes=c(1,2),proba=0.05)
res.desc$Dim.1
res.desc$Dim.2
```

#q13

```{r}
ind<-get_pca(res.pca)
```

#q14

```{r}
fviz_pca_ind(res.pca,col.ind="cos2",gradient.cols=c("#00AFBB","#E7B800","#FC4E07"),repel=TRUE)
```


#q15

```{r}
fviz_pca_ind(res.pca,pointsize="cos2",pointshape=21,fill="#E7B800",repel=TRUE)
```


#q16

#q13

```{r}
ind<-get_pca(res.pca)
```

#q14

```{r}
fviz_pca_ind(res.pca,col.ind="cos2",gradient.cols=c("#00AFBB","#E7B800","#FC4E07"),repel=TRUE)
```


#q16

```{r}
res.pca<-PCA(decathlon2,ind.sup=24:27,quanti.sup=11.12,quali.sup=13,graph=FALSE)
```
#q17
```{r}
res.pca$quanti.sup
fviz_pca_var(res.pca)
```

#q18
```{r}
res.pca$ind.sup
p<-fviz_pca_ind(res.pca,col.ind.sup="blue",repel=TRUE)
p<-fviz_add(p,res.pca$quali.sup$coord,color="red")
p
```

#q19
```{r}
fviz_pca_ind(res.pca,habillage=13,addEllipses=TRUE,ellipse.type="confidence",palette="jco",repel=TRUE)

```
#The first component positively correlated to "strength" #competations and negatively to "speed ones" The second one is #linked to endurance and pole vault.
#The right side is for better points and smaller rank, i.,e. best #players. The opposite profiles at at the left.

#When looking at the points representing "Decastar" and
#"Olympic Games", we notice that this last one has higher
#coordinates on the first axis than the first one. This shows
#an evolution in the performances of the athletes. All the
#athletes who participated to the two competitions have then
#slightly better results for the Olympic Games.
#We can see that the points which represent the same
#individual are in the same direction. For example, Sebrle got
#good results in both competition but the point which
#represents his performance during the O.G. is more extreme.
#Sebrle got more points during the O.G. than during the
#Decastar.

#Two interpretations can be made:

#1 - Athletes who participate in the O.G. are better than
#those who participate in the Decastar

#2- Athletes do their best for the O.G. (more motivated, more
#trained)

 
#The `dimdesc` tables of the description of the two principal
# our first interpretation.

#However, there is no difference between the points "Decastar"
#and "Olympic Games" for the second axis. This means that the
#athletes have improved their performance but did not change
#profile (except for Zsivoczky who went from slow and strong
#during the Decastar to fast and weak during the Olympic
#Games).

#q20

```{r}


```















